\section{International Business Practices}

\textbf{TODO: Chapter 2 Review}
\begin{itemize}
    \item Complete review package -- Anki deck and complete notes
\end{itemize}

\begin{definition}[Licensing Agreement]
    An agreement that grants permission to a company to use a product, service,
    brand name, or patent, in exchange for a fee or royalty.
\end{definition}

\begin{definition}[Exclusive Distribution Rights]
    A form of licensing agreement that grants a company the right
    to be the only distributor of a product in a specific area or country.
\end{definition}

This provides monopolistic power to the licensee. 
A good example of this would be through a streaming service 
and sports events, such as the NFL and Prime Video. \\

\begin{definition}[Franchise]
    An agreement granted to an individual or group by a company to use that 
    company's name, services, products, and marketing.
    For a fee, the franchisor provides support to the franchisee in the areas of 
    financing, operations, human resources, marketing, advertising, quality control, etc.
    A good example of this is fast food. If you open a fast food franchise, people will automatically
    come, and have expectations in mind, as advertising, ingredients, and preparation is provided by
    the franchisor.
\end{definition}

\begin{definition}[Joint Venture]
    A common type of international business, in which, a new company with shared ownership is formed 
    by two businesses, one of which is usually located in the country where the new company is established.
\end{definition}

\textbf{Joint Venture v. Merger}
A joint venture is an arrangement between two or more businesses to combine their resources. 
They choose the route of a joint venture agreement to accomplish a specific business task. 
Joint ventures, unlike mergers or acquisitions, are often temporary. Once the specific task is 
complete, the joint venture is dissolved. \\

\begin{definition}[Foreign Subsidiaries]
    Often referred to as a \textit{wholly owned subsidiary}, a 
    branch of a company that is run as an independent entity in a country outside of one 
    in which the parent company is located. \\

    The parent company often sets financial targets, and allows the subsidiary to manage its 
    day-to-day operations, so long as those targets are being met. \\
\end{definition}

\subsection{Foreign investment restrictions}
\begin{itemize}
    \item Canadian law with the greatest impact is the \textit{Investments Canada Act}.
    \item Ensures that all foreign investments are reviewed to determine how they will benefit Canada.
\end{itemize}

\subsection{Standards}
\begin{itemize}
    \item Countries have different standards for products in areas such as environmental protection, voltage, health, and safety.
    \item The ISO (International Organization for Standardization) is a network of standardization 
    groups from over 170 countries established to set quality regulations.
\end{itemize}