\section{Impact of Culture on International Business}

\begin{itemize}
    \item Culture’s role in a business venture can be as
    important as the influence of tariffs, legal
    regulations, or competition.
    \item Failure to consider culture could ruin a negotiation,
    derail a marketing campaign, cause labour unrest,
    or, in some cases, endanger one’s life.
\end{itemize}

\subsubsection{Products and Services}
\begin{itemize}
    \item Consider cultural differences to understand what
    products or services will be successful in other
    markets.
    \item Example: Canadian pork cannot be sold in Islamic countries.
    \item Example: Money and Banking \(\Rightarrow\) Saving vs. Spending
    \begin{itemize}
        \item Japan \(\Rightarrow\) Coming of Age
        \item Pilgrimages, weddings, education, etc.
    \end{itemize}
\end{itemize}

\subsection{Culture and the Labour Market}
\begin{itemize}
    \item Consider the impact of and on labour markets in other countries.
    \item \textbf{Rationalization} includes any attempt to increase a company's effectiveness or efficiency.
    \item E.g., \textit{downsizing}, \textit{cutbacks}, and \textit{layoffs}; relocating corporate functions and activities to countries that have cheaper labour.
\end{itemize}

\subsection{Child Labour and Discrimination}
Child labour is prevalent in many countries, and a cultural norm in some, exploitation is common.
On discrimination, while Canada has laws protecting discrimination, it is often difficult to prove, 
and discrimination can be made on other bases.

\subsection{Standards, Practices, and Wages}
Labour unions, vacation entitlement, accommodations like prayer, benefits, etc.
Minimum wage is not the same in all countries, and many countries do not have a fair minimum wage.

\subsection{Business Meetings and Negotiations}
Consider different styles of meetings and negotiations across cultures.
Time perception differs among cultures, with different characteristics. \\ 

Monochronic Cultures have:
\begin{itemize}
    \item Prompt beginnings and endings
    \item Scheduled breaks
    \item Deal with one agenda item at a time
    \item Rely on specific, detailed, and explicit communication
    \item Participants talk in sequence
    \item Lateness is viewed as showing a lack of respect
\end{itemize}

Whereas Polychronic Cultures have:
\begin{itemize}
    \item Flexible start and end times
    \item Breaks happen when appropriate
    \item Don't follow a rigid agenda 
    \item Often deal in broad concepts
    \item Anyone with ideas might speak
    \item Tardiness is not taken personally
\end{itemize}

