\chapter{Culture in International Business}

\section{What is Culture?}

\begin{definition}[Culture]
    Culture encompasses the knowledge, experience, beliefs, values, 
    attitudes, religion, arts, symbols, and possessions acquired by a group 
    of people over time.
\end{definition}

Some aspects of culture can be transmitted through education or by example from one generation to the next.

\begin{definition}[Subculture]
    A cultural group within a larger or predominant culture, distinguished by class, 
    ethnic background, religion, or lifestyle. Generally unified by shared beliefs and interests,
    and are not limited to immigrant populations; you can see subcultures that aren't defined by 
    one's country or origin everywhere.
\end{definition}

\begin{definition}[Counterculture]
    A culture that has values or lifestyles that oppose mainstream values and attitudes,
    usually with a view to challenge the existing norms of a prevailing society.
\end{definition}

\subsection{Canada as a multicultural nation}
\begin{itemize}
    \item Encourages and supports hundreds of different cultural groups within the overall Canadian cultural fabric.
    \item Multiculturalism as \textbf{cultural mosaic}: each of the different cultural groups exists independently as a seperate "tile" that makes up the whole picture.
\end{itemize}

\subsection{Melting Pot v. Salad Bowl}

The melting pot theory requires that immigrants assimilate in order to become one common culture. America and what it means to be American as a good example. \\ 

The salad bowl theory basically calls for us to celebrate our diversity along with our oneness. Canada and being Canadian as a good example.

\section{Business Cultures around the World}

\begin{itemize}
    \item Different countries have very different cultures shaped by various factors.
    \item Business cultures also vary greatly place to place.
    \item Anyone working in international business needs to understand and respect these differences.
    \item \textbf{Cultural intelligence:} the capability to adapt, relate, and work effectively across various culutres. 
\end{itemize}

DONE